621 - HW1 -EDA

### 2020-09-09 HW1/missing_value_eda.Rmd

```{r}
library(tidyverse)
train_df<- 
  read.csv("https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/HW1/data/moneyball-training-data.csv?token=AJP53VTYKQ4BKNZQERSMBYK7KBD52")
```

>>>>

```{r}
library(tidyverse)
train_df<- 
  read.csv("https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/HW1/data/moneyball-training-data.csv?token=AJP53VUTHKQNVGSBWE3U7KC7KDWP4")
```
